Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-28 manuscript/manuscript.Rmd
discuss figure action-X

Fig. \ref{fig:action-X} additionally shows (as a red line) the optimal escapement policy.
This policy was computed in a manner similar to how the MSY constant mortality was computed: for each escapement in a grid of 100 values between 0 and 1, 50 episodes were run using the corresponding escapement policy.
The value with the best mean episode reward was chosen as the optimal escapement value.

>>>>

Fig. \ref{fig:action-X} additionally shows (pink line) the optimal constant escapement policy and the MSY constant mortality policy (green line).
The optimal constant escapement was computed in a manner similar to how the MSY constant mortality was computed: for each escapement in a grid of 100 values between 0 and 1, 50 episodes were run using the corresponding escapement policy.
The value with the best mean episode reward was chosen as the optimal escapement value.
We observe that the DRL policy approximates the optimal constant escapement policy, with the difference of being more conservative in its harvest at high $X$ values.
This pattern can be seen in panels (C-D), where at high $X$ values, the DRL escapement mildly increases in a non-linear fashion rather than staying constant.
Finally, relative to these two policies, we observe that MSY constant mortality underfishes at high $X$ values and overfishes at low $X$ values.
